$p$-adic precision

### 2014-01-30 padicprec.tex
One paragraph on intersection of subspaces. I think that Section 5 is now almost done.

We can develop further this example and study what happens on the 
closed subset of $M_{n,n-d}(K)$ where matrices have not full rank. On
this subspace, the left kernel has dimension $< d$ and then no longer
defines a point in $\Grass(n,d)$. Nevertheless, for all integer $r <
n-d$, we can consider the subset $\mathcal V_r \subset M_{n,n-d}(K)$
of matrices whose rank are exactly rank $d$. It is locally closed in
$M_{n,n-d}(K)$ with respect to the Zariski topology and hence defines
a $K$-manifold. Furthermore, we have a mapping $\text{LK}_r : \mathcal 
V_r \to \Grass(n,n-r)$ which is differentiable and whose differential 
can be computed as before.

@@

>>>>

We can develop further this example and study what happens on the 
closed subset of $M_{n,n-d}(K)$ where matrices have not full rank. On
this subspace, the left kernel has dimension $< d$ and then no longer
defines a point in $\Grass(n,d)$. Nevertheless, for all integer $r <
n-d$, we can consider the subset $\mathcal V_r \subset M_{n,n-d}(K)$
of matrices whose rank are exactly rank $d$. It is locally closed in
$M_{n,n-d}(K)$ with respect to the Zariski topology and hence defines
a $K$-manifold. Furthermore, we have a mapping $\text{LK}_r : \mathcal 
M_r \to \Grass(n,n-r)$ which is differentiable and whose differential 
can be computed as before.

@@

We now focus on the computation of intersections. We pick $n$, $d_1$ and 
$d_2$ three nonnegative integers such that $d_1 \leq n$, $d_2 \leq n$ 
and $d_1 + d_2 \geq n$. Two subspaces of $K^n$ of dimension $d_1$ and 
$d_2$ respectively meet along a subspace of dimension at most $d_1 + d_2 
- n$. For all $d \leq d_1 + d_2 -n$, we can then define the subspace 
$\mathcal V_d$ of $\Grass(n,d_1) \times \Grass(n,d_2)$ consisting of 
pairs $(E_1, E_2)$ such that $\dim (E_1 \cap E_2) = d$ and consider the 
function $f_d : \mathcal V_d \to \Grass(n, d)$ which sends $(E_1, E_2)$ 
to $E_1 \cap E_2$. In charts, the function $f_d$ can be interpreted as
the kernel of a matrix simply because $E_1 \cap E_2$ appears as the
kernel of the canonical linear map $E_1 \oplus E_2 \to K^n$. We deduce
for this that $f_d$ is differentiable and that its differential can be
computed similarly to what we have done before.

Finally, we note that similar results hold for images of matrices and,
consequently, sums of subspaces.
